---
title: "Interest in the EVs in the UK"
author: "Claire Chang Liu & Noriko Magara"
date: "Nov. 11th, 2015"
output: html_document
fig_caption: true
bibliography: Package_Citation.bib
---

This paper looks at the interest in the Electric Vehicles in the UK. First, we will describe the process of data gathering. Then we descriptively analyze the dependent variable and independent variables. Last part will be a preliminary analysis using logistic regression models.

```{r results='hide',message=FALSE}
library(stargazer)
library(knitr)
library(Zelig)
library(rms)
library(apsrtable)
load("EVdata1.rda")
```

##Data Gathering

##Descriptive Analysis

##Logistic Regression
In this section presents our efforts to answer the question, "Who are more/less likely to be interested in the EVs". Since the dependent variable is a binary variable, i.e. respondents having an interest in the EVs or not, we adopt logistic regression models here.

Nine independent variables are categorized into four groups. Socio-economic variables include age, sex, gross annual income level, and education level. The second group includes having driver's license or not, and the number of cars available to the household, which to some extent describe the respondents' potential to buy a new car.The third one is household-level variables, including household size and whether or not having depedent children. The last one is region. (The UK has 11 regions in total. However, our preliminary analysis suggests that, using London as the baseline, only Scotland is significantly different. Therefore, we only include "Scotland" in the regression.)

We only include socio-economic variables in our base model (regression 1) and add in a new group of independent variables each time. The results are as following:

```{r echo=F, warning=F, message=F, error=F}
# Estimate model-1 (AGE & SEX & INCOME & Education)
L1 <- lrm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high + degree, 
           EVINTEREST)

# Estimate model-2 (AGE & SEX & INCOME & Education & LICENCE & Number of Cars)
L2 <- lrm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high + degree + licence + NumCar, EVINTEREST)

# Estimate model-3 (AGE & SEX & INCOME & Education & LICENCE & Number of Cars % Number of Children)
L3 <- lrm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high + degree + licence + NumCar + DVHsize + havechildren,
          EVINTEREST)

# Estimate model-4 (AGE & SEX & INCOME & Education & LICENCE & Number of Cars & Number of Children & Scotland)
L4 <- lrm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high + degree + licence + NumCar + DVHsize + havechildren + Scotland,
          EVINTEREST)
```

```{r echo=F, warning=F, message=F, error=F}
labels <- c('Age', 'Male', 'Income: low-middle', 'Income: high-middle', 'Income: high', 
            'College degree', 'Drivers licence', '# of cars', "Size of household", 'Having dependent children', 'Scotland', '(Intercept)') 
stargazer::stargazer(L1, L2, L3, L4,  type="text", covariate.labels = labels,
                     digits = 2, title ="Step-wise Modelling")
```

As the table above shows, all models are significant at 99% level. Except for the two variables, size of household and having dependent children or not, all other variables are statistically signifcant as well. The fact that household-related variables are effective predictors at macro level, but not at micro level, may suggest a neighborhood effect, but it is beyond the scope of this paper.

Based on this analysis, we leave out the two household-related variables and use the following formula.

$$Prob(Interested-in-EVs)= \beta_{0}+\beta_{1}Age+\beta_{2}Male+\beta_{3}Lowmid$$

$$+\beta_{4}Highmid+\beta_{5}High+\beta_{6}College+\beta_{7}License+\beta_{8}Numcar+\beta_{9}Scotland$$
```{r echo=F, warning=F, message=F, error=F}
L5 <- lrm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high + degree 
          + licence + NumCar + Scotland,
          EVINTEREST)
stargazer::stargazer(L5,  type="text", covariate.labels = labels,
                     digits = 2, title ="Interests in EVs")
```



##Discussion

##Reference
