---
title: "Determinants of Interest in the EVs in the UK"
author: "Claire Chang Liu & Noriko Magara"
date: "Nov. 13th, 2015"
output:
  pdf_document: 
    fig_caption: yes
    number_sections: yes
bibliography: citation.bib
---

This paper examines the determinants of interest in electric vehicles (EVs) in the UK. 
First, we will describe the process of data gathering. 
Then we descriptively analyze the dependent variable and independent variables, and use logistic regression models to indentify the correlations.
Last part will be a brief discussion of the results of the analysis.

```{r results='hide',echo=F, warning=F, message=F, error=F}
### set working directory
setwd("E:\\—ßœ∞œ‡πÿ\\R\\Collaborative-Data-Analysis-Assignment2\\Assignment3")


library(stargazer)
library(knitr)
library(Zelig)
library(rms)
library(captioner)
library(foreign)
library(dplyr)
  
figcap <- captioner(prefix = "Figure", auto_space = TRUE, levels = 1, type = NULL)
tablecap <-captioner(prefix = "Table", auto_space = TRUE, levels = 1, type = NULL)
```

# Data Gathering
This analysis is based on survey data in the UK called ["Opinions and Lifestyle Survey, Electric Vehicles Module, February 2014 and February 2015"](https://discover.ukdataservice.ac.uk/Catalogue/?sn=7571&type=Data%20catalogue) [@UKDATA]. 
Note that [registration](http://ukdataservice.ac.uk/get-data/how-to-access/registration) is required to download the dataset from the UK Data Service website above.
After logging in and agreeing with the terms of conditions, the datasets are available for download in STATA or other format.
The registration process may take a few days. 
However, other documents (e.g. questionnaire, brief summary) are available at the link above without registration.
This module comes with two datasets: survey results from 2014 and 2015. 
For our study, we use both survey years by combining both datasets together. 

```{r echo=F, warning=F, message=F, error=F}
source("data_cleanup.R")
```

# Descriptive Analysis
## Variables
The list of variables are shown in the table below.

```{r echo=F, warning=F, message=F, error=F, results='asis'}
Names <- c("EVinterest", "RAGE", "Male", "inccat", "degree", "licence", 
           "NumCar", "DVHsize", "havechildren", "Scotland")
Types <- c("dummy", "continuous", "dummy", "categorical", "dummy", 
           "dummy", "continuous", "continuous", "dummy", "dummy")
Descriptions <- c("Whether the respondent is interested in EVs or not", 
                  "Respondent's age",
                  "Respondent's sex",
                  "Respondent's income in 4 categories (low, low-mid, high-mid, high)",
                  "Whether the respondent is a college graduate or not",
                  "Whether the respondent has a valid drivers licence or not",
                  "Number of cars in the respondent's household",
                  "Respondent's household size",
                  "Whether the Respondent has children or not",
                  "Whether the Respondent lives in Scotland or not")
vartable <- cbind(Names, Types, Descriptions)
kable(vartable, caption="List of Variables")
```


## Summary statistics
* **EVinterest**: `r round(mean(EVINTEREST$EVinterest)*100, digits=2)` % of respondents are interested in EVs

* **RAGE**: Mean=`r round(mean(EVINTEREST$RAGE), digits=2)`, Standard deviation=`r round(sd(EVINTEREST$RAGE), digits=2)`.
The distribution of age is shown in the figure below.

* **Male**: `r round(mean(EVINTEREST$Male)*100, digits=2)` % of respondents are male

* **inccat**: distribution is shown in the table and the figure below. 
The thresholds of each category are based on 25, 50, 75 percentile gross income from [Survey of Personal Incomes 2012-13 in the UK](https://www.gov.uk/government/uploads/system/uploads/attachment_data/file/399041/Table_3_1_a_13.xls)(@UKincome).

```{r echo=F, warning=F, message=F, error=F, results='asis'}
inccatcount <- table(EVINTEREST$inccat)
Percentage <- round(inccatcount/length(EVINTEREST$inccat)*100, digits=2)
Income <- c('Low', 'Low-Mid', 'High-Mid', 'High')
Range <- c('Below 14,559GBP', '14,560GBP~20,799GBP', '20,800GBP~25,999GBP', '26,000GBP and Above')
inccatsummary <- cbind(Income, Range, Percentage)
kable(inccatsummary, caption="Distribution of Income")
```

* **degree**: `r round(mean(EVINTEREST$degree)*100, digits=2)` % of respondents have college degree

* **licence**: `r round(mean(EVINTEREST$licence)*100, digits=2)` % of respondents have valid drivers licence

* **NumCar**: Mean=`r round(mean(EVINTEREST$NumCar), digits=2)`, Standard deviation=`r round(sd(EVINTEREST$NumCar), digits=2)`. The distribution of the number of cars in respondent's household is shown in the figure below.

* **DVHsize**: Mean=`r round(mean(EVINTEREST$DVHsize), digits=2)`, Standard deviation=`r round(sd(EVINTEREST$DVHsize), digits=2)`. The distribution of household size is shown in the figure below.

* **havechildren**: `r round(mean(EVINTEREST$havechildren)*100, digits=2)` % of respondents have children

* **Scotland**: `r round(mean(EVINTEREST$Scotland)*100, digits=2)` % of respondents lives in Scotland

```{r echo=F, warning=F, message=F, error=F, fig.cap="Distribution of respondent's age", fig.height=4}
hist(EVINTEREST$RAGE, main=" ",
     xlab="Age", ylab="Frequency", 
     xlim=c(10,100))
axis(side=1, at=seq(0,100, 10))
```

```{r echo=F, warning=F, message=F, error=F, fig.cap="Distribution of respondent's income", fig.height=4}
inctable <-table(EVINTEREST$inccat)
barplot(inctable, ylab="Frequnecy",
        names.arg=c("Low", "Low-Mid", "High-Mid", "High"))
mtext(side=1, "Gross Annual Income", line=2)
mtext(side=1, "(Low:~14,559 /Low-Mid:14,560~20,799 /High-Mid:20,800~25,999 /High: 26,000+)", line=3)
```

```{r echo=F, warning=F, message=F, error=F, fig.cap="Distribution of number of cars", fig.height=4}
cartable <-table(EVINTEREST$NumCar)
barplot(cartable, 
     xlab="Number of Cars", ylab="Frequency")
```

```{r echo=F, warning=F, message=F, error=F, fig.cap="Distribution of household size", fig.height=4}
Hsizetable <- table(EVINTEREST$DVHsize)
barplot(Hsizetable, main="Household size", 
        xlab="Household size", ylab="Frequency")
```

\newpage

#Logistic Regression
##Modelling
This section presents our efforts to answer the question, "Who are more/less likely to be interested in EVs". Since the dependent variable is a binary variable, i.e. respondents having an interest in EVs or not, we adopt logistic regression models here.

Nine independent variables are categorized into four groups. Socio-economic variables include age, sex, gross annual income level, and education level. The second group includes having driver's license or not, and the number of cars available to the household, which to some extent describe the respondents' potential to buy a new car. The third one is household-level variables, including household size and whether or not having depedent children. The last one is region. (The UK has 11 regions in total. However, our preliminary analysis suggests that, using London as the baseline, only Scotland is significantly different. Therefore, we only include "Scotland" in the regression.)

We only include socio-economic variables in our base model (regression 1) and add in a new group of independent variables each time. As the results in table 3 show, all models are significant at 99% level. Except for the two variables, size of household and having dependent children or not, all other variables are statistically signifcant as well. The fact that household-related variables are effective predictors at macro level, but not at micro level, may suggest a neighborhood effect, but it is beyond the scope of this paper.

```{r echo=F, warning=F, message=F, error=F}
# Estimate model-1 (AGE & SEX & INCOME & Education)
L1 <- lrm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high + degree, 
           EVINTEREST)

# Estimate model-2 (AGE & SEX & INCOME & Education & LICENCE & Number of Cars)
L2 <- lrm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high + degree 
          + licence + NumCar, EVINTEREST)

# Estimate model-3 (AGE & SEX & INCOME & Education & LICENCE & Number of Cars % Number of Children)
L3 <- lrm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high + degree 
          + licence + NumCar + DVHsize + havechildren, EVINTEREST)

# Estimate model-4 (AGE & SEX & INCOME & Education & LICENCE & Number of Cars & Number of Children & Scotland)
L4 <- lrm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high + degree 
          + licence + NumCar + DVHsize + havechildren + Scotland, EVINTEREST)
```

```{r echo=F, warning=F, message=F, error=F, results='asis'}
labels <- c('Age', 'Male', 'Income: low-middle', 'Income: high-middle', 'Income: high', 
            'College degree', 'Drivers licence', 'Number of cars', "Size of household", 
            'Having dependent children', 'Scotland', '(Intercept)') 

stargazer::stargazer(L1, L2, L3, L4,  type="latex", header=F, covariate.labels = labels,
                     digits = 2, title="Step-wise Modelling")
```

\newpage

Based on this analysis, we leave out the two household-related variables and use the following formula.

$$\ln{(\frac{p} {1-p})}=\beta_{0}+\beta_{1}Age+\beta_{2}Male+\beta_{3}Lowmid+\beta_{4}Highmid+\beta_{5}High+\beta_{6}College$$
$$+\beta_{7}license+\beta_{8}NumCar+\beta_{9}Scotland$$

Where $p$ is the probability of being interested in EVs. The estimated model is shown in table 4.

```{r echo=F, warning=F, message=F, error=F, results='asis'}
finallabels <- c('Age', 'Male', 'Income: low-middle', 'Income: high-middle', 'Income: high', 
            'College degree', 'Drivers licence', 'Number of cars', 'Scotland', '(Intercept)') 
L5 <- lrm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high + degree 
          + licence + NumCar + Scotland,
          EVINTEREST)
stargazer::stargazer(L5, type="latex", header=F, covariate.labels = finallabels,
                     digits = 2, title="Interests in EVs")
```

The model is statistically significant at 99% level and five out of the seven variables are significant at 95% level. On average, males are more likely to be interested in EVs. Having a college degree or driver's license also increases the likelihood of being interested. The number of cars is positively relative to the likelihood, suggesting that people who already have the "basics" are more likely to consider EVs. However, being in Scotland reduces this likelihood. 

The less significant variables are age and income level. Age is negatively relative to the likelihood of being interested, meaning that younger people are more likely to have an interest in EVs. Interestingly, income level seems not to matter much. Using the lowest quartile group as the baseline, only the highest quartile group is significantly different at 90% level. Nevertheless, results from regression 1 shows that income level (at least when comparing the highest quartile to the lowest quartile) is statistically significant at 99% level. The decrease in significance is due to the correlation between income level, and having driver's license and number of cars available. 

##Comparison of Predicted Probabilities by Group
In addition to the odds ratio provided in the regression output, we want to be more specific with the size of effects of the seven independent variables. Therefore, the ranges of probability based on the variation of different variables are provided as following.

$$Pr(Interested)=\frac{1} {1 + e^{\boldsymbol{\beta_k \cdot x_i}}}$$

```{r echo=F, warning=F, message=F, error=F, fig.cap="Predicted Probability of Having an Interest in EVs by Age and Sex", fig.height=5.5}
ZP <- zelig(EVinterest ~ RAGE + Male + lowermiddle + highermiddle + high 
             + degree + licence + NumCar  + Scotland, 
             cite = FALSE, data = EVINTEREST, model = 'logit')
setZP1 <- setx(ZP, RAGE = 20:95, Male=0)
simZP1 <- sim(ZP, x = setZP1)
plot(simZP1, xlab="Age", ylab="Predicted Probability", col=rgb(1,0,0,0.15), 
     ylim=c(0,0.4), xlim=c(20,100))
par(new=T)
setZP1 <- setx(ZP, RAGE = 20:95, Male=1)
simZP1 <- sim(ZP, x = setZP1)
plot(simZP1, xlab="Age", ylab="Predicted Probability", col=rgb(0,0,1,0.15), 
     ylim=c(0,0.4), xlim=c(20,100))
legend("topright", c("Male","Female"),lwd=1, col=c("blue","red"))
```

\newpage

Figure 5 shows the predicted probability of having an interest in EVs by age and sex. Regardless of age, males show a greater interest than females. Even though the variation among males is larger too, the difference in probability is on average about 5 percentage points. The linear relationship between age and this probability is clearly demostrated here as well. Younger people are more likely to be interested than older people.

Table 5-9 summarize predicted probabilities of having an interest in EVs of different groups and allow us to know the differences between groups. 

* By Income Level & Sex: predicted for those people with mean age, valid licence, college degree, a car, and who doesn't live in Scotland.

```{r echo=F, warning=F, message=F, error=F}
# same model with glm
LPred <- glm(EVinterest ~ RAGE + Male + lowermiddle + highermiddle +high 
             + degree + licence + NumCar + Scotland, 
             data = EVINTEREST, family = 'binomial')

# predicted probability by income group & sex
fitted1 <- with(EVINTEREST,
                data.frame(RAGE=mean(RAGE), Male=c(1,1,1,1),  
                           lowermiddle=c(0,1,0,0), highermiddle=c(0,0,1,0), 
                           high=c(0,0,0,1), licence=1, degree=1, NumCar=1, Scotland=0))
fitted1$predicted <- predict(LPred, newdata = fitted1, type = 'response')
fitted1$predicted <- round(fitted1$predicted*100, digits=2)
fitted2 <- with(EVINTEREST,
                data.frame(RAGE=mean(RAGE), Male=c(0,0,0,0),  
                           lowermiddle=c(0,1,0,0), highermiddle=c(0,0,1,0), 
                           high=c(0,0,0,1), licence=1, degree=1, NumCar=1, Scotland=0))
fitted2$predicted <- predict(LPred, newdata = fitted2, type = 'response')
fitted2$predicted <- round(fitted2$predicted*100, digits=2)

Incomegroup <- c("Lowest quartile", "Second lowest quartile", "Second highest quartile", "Highest quartile")

byincomesex <- cbind(Incomegroup, fitted1$predicted, fitted2$predicted)

kable(byincomesex, caption="Probability by Income Level & Sex", 
      col.names = c("Income Level", "Male", "Female"))
```

* By Education Level & Sex: predicted for those people with mean age, lower-middle income, valid licence, a car, and who doesn't live in Scotland.

```{r echo=F, warning=F, message=F, error=F}
# predicted probability by educ group & sex
fitted3 <- with(EVINTEREST,
                data.frame(RAGE=mean(RAGE), Male=1, lowermiddle=1, 
                           highermiddle=0, high=0,
                           licence=1, degree=c(1,0), NumCar=1, Scotland=0))
fitted3$predicted <- predict(LPred, newdata = fitted3, type = 'response')
fitted3$predicted <- round(fitted3$predicted*100, digits=2)
fitted4 <- with(EVINTEREST,
                data.frame(RAGE=mean(RAGE), Male=0, lowermiddle=1, 
                           highermiddle=0, high=0,
                           licence=1, degree=c(1,0), NumCar=1, Scotland=0))
fitted4$predicted <- predict(LPred, newdata = fitted4, type = 'response')
fitted4$predicted <- round(fitted4$predicted*100, digits=2)

Edugroup <- c("At least have a college degree", "Do not have a college degree")

byedusex <- cbind(Edugroup, fitted3$predicted, fitted4$predicted)

kable(byedusex, caption="Probability by Education Level & Sex", 
      col.names = c("Education Level", "Male", "Female"))
```

* By License Status & Sex: predicted for those people with mean age, lower-middle income, college degree, a car, and who doesn't live in Scotland.

```{r echo=F, warning=F, message=F, error=F}
# predicted probability by licence group & sex
fitted5 <- with(EVINTEREST,
                data.frame(RAGE=mean(RAGE), Male=1, lowermiddle=1, 
                           highermiddle=0, high=0,
                           licence=c(1,0), degree=1, NumCar=1, Scotland=0))
fitted5$predicted <- predict(LPred, newdata = fitted5, type = 'response')
fitted5$predicted <- round(fitted5$predicted*100, digits=2)
fitted6 <- with(EVINTEREST,
                data.frame(RAGE=mean(RAGE), Male=0, lowermiddle=1, 
                           highermiddle=0, high=0,
                           licence=c(1,0), degree=1, NumCar=1, Scotland=0))
fitted6$predicted <- predict(LPred, newdata = fitted6, type = 'response')
fitted6$predicted <- round(fitted6$predicted*100, digits=2)

ligroup <- c("Have driver's license", "Do not have driver's license")

bylisex <- cbind(Edugroup, fitted5$predicted, fitted6$predicted)

kable(bylisex, caption="Probabilities by Driver's License Status & Sex", 
      col.names = c("License Status", "Male", "Female"))
```

* By Number of Cars & Sex: predicted for those people with mean age, lower-middle income, college degree, valid licence, and who doesn't live in Scotland.

```{r echo=F, warning=F, message=F, error=F}
# predicted probability by NumCar & sex
fitted7 <- with(EVINTEREST,
                data.frame(RAGE=mean(RAGE), Male=1, lowermiddle=1, 
                           highermiddle=0, high=0, licence=1, degree=1, 
                           NumCar=c(0,1,2,3), Scotland=0))
fitted7$predicted <- predict(LPred, newdata = fitted7, type = 'response')
fitted7$predicted <- round(fitted7$predicted*100, digits=2)
fitted8 <- with(EVINTEREST,
                data.frame(RAGE=mean(RAGE), Male=0, lowermiddle=1, 
                           highermiddle=0, high=0, licence=1, degree=1, 
                           NumCar=c(0,1,2,3), Scotland=0))
fitted8$predicted <- predict(LPred, newdata = fitted8, type = 'response')
fitted8$predicted <- round(fitted8$predicted*100, digits=2)

bycarsex <- cbind(fitted7$NumCar, fitted7$predicted, fitted8$predicted)

kable(bycarsex, caption="Probabilities by Number of Cars & Sex", 
      col.names = c("Number of Cars", "Male", "Female"))
```

* By Region & Sex: predicted for those people with mean age, lower-middle income, college degree, valid licence, and a car.

```{r echo=F, warning=F, message=F, error=F}
# predicted probability by region & sex
fitted9 <- with(EVINTEREST,
                data.frame(RAGE=mean(RAGE), Male=1, lowermiddle=1, 
                           highermiddle=0, high=0, licence=1, degree=1, 
                           NumCar=1, Scotland=c(1,0)))
fitted9$predicted <- predict(LPred, newdata = fitted9, type = 'response')
fitted9$predicted <- round(fitted9$predicted*100, digits=2)
fitted10 <- with(EVINTEREST,
                data.frame(RAGE=mean(RAGE), Male=0, lowermiddle=1, 
                           highermiddle=0, high=0, licence=1, degree=1, 
                           NumCar=1, Scotland=c(1,0)))
fitted10$predicted <- predict(LPred, newdata = fitted10, type = 'response')
fitted10$predicted <- round(fitted10$predicted*100, digits=2)

scotgroup <- c("In Scotland", "In other regions")

byscotsex <- cbind(scotgroup, fitted9$predicted, fitted10$predicted)

kable(byscotsex, caption="Probabilities by Region & Sex", 
      col.names = c("Region", "Male", "Female"))
```


#Discussion and Limitations
In general, interest in EVs is rather limited. Among all respondents, only 18.48% are interested. This, on the other hand, suggests the need to better understand the factors related to the interest in EVs, and this is what motivated our research too.

Above analysis shows that the variations among different groups are quite large. For instance, people having a college degree, on average, have a probability of 30.7% to be interested in EVs, while people without a degree only have a probability of 14.5%. This kind of variation (especially the one related to education level) is actually a good sign, suggesting that interest in EVs could be potentially increased. Promotion of EVs should give more attention to the needs and comsumption patterns of low-interest groups. 

However, this also leads to one of the limitations of this paper, not being able answer why different groups show different levels of interest. This question is very hard, not just because we do not have more detailed surveys, but also because different groups may be systematically different in many unobeserved ways. Even though, we will still attempt to make contributions on this question in our final paper.

Another limitation is due to the design of the survey, which did not exclude respondents who are not interested in buying cars in genereal. Therefore, varialbes, including having driver's license and number of cars available, need to be interpreted with great caution. The low interest shown in groups without driver's license or cars might not be caused by their lack of interest in EVs, but by their lack of interest in cars.

Lastly, $R^2$ of the model is only 0.12, meaning that these variables only explain 12% of the variations in the probability of having an interest in EVs. Partly, this is because of a lack of available information, as it is impossible to survey everything. Partly, attitudes are just not easy to explain, because they could be influenced by countless factors, sometimes as trivial as an image or some careless words. Nevertheless, we believe that there are patterns and these patterns are what we should better understand if EVs are to be further promoted.

\textcolor{white}{
@CiteR
@R-captioner	
@R-dplyr	
@R-foreign 
@R-knitr	
@R-repmis	
@R-rms	
@R-stargazer 
@R-Zelig
}